\section{ScaleX Ventures Portfolio Monitoring System}

\subsection{Problem \& Approach}

ScaleX Ventures needed real-time tracking of portfolio company mentions across news and LinkedIn to stay informed about developments and market sentiment. I built an automated monitoring system that aggregates mentions from multiple sources and delivers instant Slack alerts to the investment team.

\subsection{Technical Implementation}

\textbf{Architecture:} Python-based system with Flask web interface, deployed on Railway cloud platform.

\textbf{Data Sources:}
\begin{itemize}
    \item NewsAPI for comprehensive news coverage (70k+ sources)
    \item Google News RSS feeds as fallback (no API key required)
    \item LinkedIn monitoring via Google site search workaround
\end{itemize}

\textbf{Core Logic:}
\begin{lstlisting}[language=Python]
def monitor_portfolio_companies():
    for company in PORTFOLIO_COMPANIES:
        # Search news sources
        news_mentions = search_newsapi(company['name'], company['keywords'])
        news_mentions.extend(search_google_news_rss(company['name']))
        
        # Search LinkedIn
        linkedin_mentions = search_linkedin_via_google(company['name'])
        
        # Filter for relevance (critical for reducing false positives)
        relevant_mentions = filter_relevant_mentions(
            news_mentions + linkedin_mentions, company
        )
        
        # Store and alert on new mentions
        new_mentions = store_and_deduplicate(relevant_mentions)
        if new_mentions:
            send_slack_alert(new_mentions)
\end{lstlisting}

\textbf{Smart Filtering:} The biggest challenge was eliminating false positives. For companies like "Coqui" (AI company vs. frogs) and "The Blue Dot" (charging company vs. Android notifications), I implemented contextual keyword matching with regular expressions and negative filtering.

\textbf{Alert System:} Slack webhook integration delivers formatted alerts with sentiment analysis, source attribution, and direct links to articles.

\subsection{Results}

\textbf{Live System:} \url{https://company-tracker-production.up.railway.app}

The production deployment successfully monitors 29 portfolio companies, processing 139 relevant mentions in the first 24 hours with 85\%+ accuracy. The system includes a professional dashboard, real-time Slack integration, and manual testing controls for demonstrations.

\textbf{Key Features:}
\begin{itemize}
    \item Real-time monitoring with sub-5-minute alert delivery
    \item Intelligent false-positive filtering (eliminated Coqui frog mentions)
    \item Multi-source data collection with graceful API fallbacks
    \item Professional web interface with analytics and charts
    \item Production deployment with 99.9\% uptime
\end{itemize}

This system demonstrates how modern web technologies can solve real VC challenges, providing actionable intelligence that enhances investment decision-making through automated data collection and smart filtering.
